Predicting Political Support in the United States

### 2024-03-16 output/paper.qmd
Add model math

@@

@@

# Results

>>>>

Therefore the model we are interested in is:

$$
\begin{aligned}
y_i|\pi_i & \sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0 +\beta_1 \times \mbox{age_group}_i + \beta_2 \times \mbox{gender}_i +\beta_3 \times \mbox{race}_i + \beta_4 \times \mbox{religion}_i \\
\beta_0 & \sim \mbox{Normal}(0, 2.5)\\
\beta_1 & \sim \mbox{Normal}(0, 2.5)\\
\beta_2 & \sim \mbox{Normal}(0, 2.5)\\
\beta_3 & \sim \mbox{Normal}(0, 2.5)\\
\beta_4 & \sim \mbox{Normal}(0, 2.5)
\end{aligned}
$$
Where $y_i$ is whether they voted for Biden or not in the 2020 election, $\mbox{age_group}_i$ is the age group the respondent falls in, $\mbox{gender}_i$ is the gender of the respondent, $\mbox{race}_i$ is the race of the respondent, and $\mbox{religion}_i$ is the relgion of the respondent.

@tbl-modelsummarycultural shows a model summary for this model, this will be dicussed further in the [results](#results) section.

@@

$$
\begin{aligned}
y_i|\pi_i & \sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0 +\beta_1 \times \mbox{education}_i + \beta_2 \times \mbox{student_loan_status}_i +\beta_3 \times \mbox{household_gun_ownership}_i \\
\beta_0 & \sim \mbox{Normal}(0, 2.5)\\
\beta_1 & \sim \mbox{Normal}(0, 2.5)\\
\beta_2 & \sim \mbox{Normal}(0, 2.5)\\
\beta_3 & \sim \mbox{Normal}(0, 2.5)
\end{aligned}
$$

where $y_i$ is whether they voted for Biden or not in the 2020 election, $\mbox{education}_i$ is the highest education the respondent completed, $\mbox{student_loan_status}_i$ is if the respondent has student loans, and $\mbox{household_gun_ownership}_i$ is if the respondent or someone within their household owns a gun.

@tbl-modelsummaryimportances shows a model summary for this model, this will be dicussed further in the [results](#results) section.

@@

# Results {#results}
